Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-12-07 doc/om-paper/paper.tex
wibbles sitting with Ben.

\begin{itemize}
\item {\bf $\OM(0)$}: $g$ broadcasts a value to each lieutenant, and the lieutenants return the value received (or $\ERR$).
\item {\bf $\OM(m)$, $m > 0$}:
  \begin{enumerate}
  \item $g$ broadcasts a value to each lieutenant, $l$.
  \item\label{om:two} Let $l_v$ be the value received by $l \in L$ from $g$. Then for each $l$, execute $\OMH(m-1)$, assigning $l$ to be the general and $L \setminus \{l\}$ to be the lieutenants. $l$ sends $l_v$ or $R$, if $l_v = \ERR$.
  \item For each lieutenant $l \in L$, remove all $\ERR$ values received in Step~\ref{om:two} from executing $OHM(m-1)$. Compute the majority value over the remaining values, or $V$ if there is no majority. If the majority value is $R$, return $E$.
  \end{enumerate}
\end{itemize}

@@

We have implemented $\OMH(1)$ (as well as many variants, described in Section~\ref{sec:modular}) in the Symbolic Analysis Laboratory~\cite{SAL} (SAL) language. The verification is also carried out in SAL, which contains a suite of model-checkers. In our work, we use infinite-state (SMT-based) $k$-induction~\cite{Moura_boundedmodel,Armando-et-al}.

We have chosen to follow Rushby~\cite{Rushby:OM1} in ``unrolling'' the communication among lieutenants into two sets of logical nodes: relays and receivers. A special node called the source takes the place of the general above. Thus, for example, in the case where 4 nodes execute $\OMH(1)$, our model consists of one source, three relays, and three receivers. We model communication through one-way, typed channels. The source broadcasts a message to each relay which, in turn, each broadcast their messages to all receivers.

>>>>

\begin{itemize}
\item {\bf $\OMH(0)$}: $g$ broadcasts a value to each lieutenant, and the lieutenants return the value received (or $\ERR$).
\item {\bf $\OMH(m)$, $m > 0$}:
  \begin{enumerate}
  \item $g$ broadcasts a value to each lieutenant, $l$.
  \item\label{om:two} Let $l_v$ be the value received by $l \in L$ from $g$. Then for each $l$, execute $\OMH(m-1)$, assigning $l$ to be the general and $L \setminus \{l\}$ to be the lieutenants. $l$ sends $l_v$ or $R$, if $l_v = \ERR$.
  \item For each lieutenant $l \in L$, remove all $\ERR$ values received in Step~\ref{om:two} from executing $\OMH(m-1)$. Compute the majority value over the remaining values, or $V$ if there is no majority. If the majority value is $R$, return $E$.
  \end{enumerate}
\end{itemize}

@@

We have implemented $\OMH(1)$ (as well as the variants, described in Section~\ref{sec:modular}) in Symbolic Analysis Laboratory (SAL)~\cite{SAL}. SAL contains a suite of model-checkers. In our work, we use infinite-state (SMT-based) $k$-induction~\cite{Moura_boundedmodel,Armando-et-al}.

We follow Rushby~\cite{Rushby:OM1} in ``unrolling'' the communication among lieutenants into two sets of logical nodes: \emph{relays} and \emph{receivers}. Relays \lee{finish}

We refer to the general as the \emph{source}. Thus, for example, in the case where four nodes execute $\OMH(1)$, our model consists of one source, three relays, and three receivers. We model communication through one-way, typed channels. The source broadcasts a message to each relay which, in turn, each broadcast their messages to all receivers.
